Parameter space representation of Pareto set

### 2013-09-26 concepts.tex
commented comments

{[}BISOGNEREBBE INTRODURRE IL CONCETTO DI FEASIBILITY{]}
\begin{defn}
\emph{\label{pers02.def:Pareto-set}Pareto set}

@@

!!! FORSE NON E' VERO CHE NOI WILL INVESTIGATE .... FORSE IL PERIODO
PRECEDENTE NON VA PIU' BENE PERCHE' NON TROVA RISCONTRO NEL RESTO
DELLA TRATTAZIONE

@@

We also consider, in measuring how much iteresting a region is, the
``innovation'' that it adds. If, during a design space exploration,
a Pareto front is temporarily calculated, adding a new Pareto front
point near to the previous ones is not a considerable ``innovation'',
because the way it fulfils the objectives is very similar to other
already evaluated configurations. On the contrary, adding a new Pareto
front point that is very distant from previous ones is remarkable,
because it let the experimenter realize that the objectives can be
fulfilled in a completely different way from what he already found
during exploration. So a region will be evaluated ineresting as much
as how different are its added Pareto front points from the ones already
found.
\begin{rem}
We will consider only parameters $p_{i}$ with ordering, i.e. such
that, if $P_{i}$ is a domain, $\forall a,b\in P_{i}$ it is possible
to say $a<b$ or $a=b$ or $a>b$.
\end{rem}
{[}TODO: DESCRIVERE COME SI PENSA DI TRATTARE GLI SCENARI IN CUI ESISTONO
PARAMETRI SENZA ORDINAMENTO{]}
\begin{defn}
\emph{Parameter interval}

>>>>

%{[}BISOGNEREBBE INTRODURRE IL CONCETTO DI FEASIBILITY{]}
\begin{defn}
\emph{\label{pers02.def:Pareto-set}Pareto set}

@@

@@

We also consider, in measuring how much iteresting a region is, the
``innovation'' that it adds. If, during a design space exploration,
a Pareto front is temporarily calculated, adding a new Pareto front
point near to the previous ones is not a considerable ``innovation'',
because the way it fulfils the objectives is very similar to other
already evaluated configurations. On the contrary, adding a new Pareto
front point that is very distant from previous ones is remarkable,
because it let the experimenter realize that the objectives can be
fulfilled in a completely different way from what he already found
during exploration. So a region will be evaluated ineresting as much
as how different are its added Pareto front points from the ones already
found.
\begin{rem}
We will consider only parameters $p_{i}$ with ordering, i.e. such
that, if $P_{i}$ is a domain, $\forall a,b\in P_{i}$ it is possible
to say $a<b$ or $a=b$ or $a>b$.
\end{rem}
%TODO: DESCRIVERE COME SI PENSA DI TRATTARE GLI SCENARI IN CUI ESISTONO
%PARAMETRI SENZA ORDINAMENTO{]}
\begin{defn}
\emph{Parameter interval}
